Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-10-01 submission/NatCom_abstract_file.tex
pass to address most of the presubmission comments for nat comm

In many applications, one works with neural network models trained by someone else.
For such \emph{pretrained models}, one often does not have access to training data or test data.
Moreover, one may not know details about the model, e.g., the specifics of the training data, the loss function, the hyperparameter values, etc.
Given one or many pretrained models, can one say anything about the expected performance or quality of the models?
Here, we address this question by providing a detailed meta-analysis of hundreds of publicly-available pretrained models.
We examine norm based capacity control metrics as well as power law based metrics from the recently-developed Theory of Heavy-Tailed Self Regularization.
We find that norm based metrics correlate well with reported test accuracies for well-trained models, but that they often can not distinguish well-trained versus poorly-trained models.
We also find that power law based metrics do much better---qualitatively better at discriminating well-trained versus poorly-trained models, and quantitatively better at discriminating among series of well-trained models.
These methods can be used to identify when a pretrained neural network has problems that can not be detected simply by examining training/test accuracies.

>>>>

In many applications, one works with neural network models trained by someone else.
For such pretrained models, one may not have access to training data or test data.
Moreover, one may not know details about the model, e.g., the specifics of the training data, the loss function, the hyperparameter values, etc.
Given one or many pretrained models, it is a challenge to say anything about the expected performance or quality of the models.
Here, we address this challenge by providing a detailed meta-analysis of hundreds of publicly-available pretrained models.
We examine norm based capacity control metrics as well as power law based metrics from the recently-developed Theory of Heavy-Tailed Self Regularization.
We find that norm based metrics correlate well with reported test accuracies for well-trained models, but that they often can not distinguish well-trained versus poorly-trained models.
We also find that power law based metrics do much better---qualitatively better at discriminating well-trained versus poorly-trained models, and quantitatively better at discriminating among series of well-trained models.
These methods can be used to identify when a pretrained neural network has problems that can not be detected simply by examining training/test accuracies.

### 2020-10-01 submission/NatCom_appendix.tex
pass to address most of the presubmission comments for nat comm

\section{Reproducibility Appendix}
\label{sxn:appendix}

In this appendix, we provide more details on several issues that are important for the reproducibility of our results.
%
All of our computations were performed with the \emph{WeightWatcher} tool (version 0.2.7)~\cite{weightwatcher_package}.
More details and more results are available in an accompanying github repository~\cite{kdd20_sub_repo}.

\subsection{Reproducibility Considerations}

\paragraph{SVD of Convolutional 2D Layers.}

There is some ambiguity in performing spectral analysis on Conv2D layers.  
Each layer is a 4-index tensor of dimension $(w,h,in,out)$, with an $(w\times h)$ filter (or kernel) and $(in, out)$
channels. When $w=h=k$, it gives $(k\times k)$ tensor slices, or \emph{pre-Activation Maps} $\mathbf{W}_{i,L}$ of dimension $(in\times out)$ each. 
%
We identify 3 different approaches for running SVD on a Conv2D layer:
\begin{enumerate}
\item run SVD on each pre-Activation Map $\mathbf{W}_{i,L}$, yielding $(k\times k)$ sets of $M$ singular values;
\item stack the maps into a single matrix of, say, dimension $((k\times k\times out)\times in)$, and run SVD to get $in$ singular values;
\item compute the 2D Fourier Transform (FFT) for each of the $(in, out)$ pairs, and run SVD on the Fourier coefficients~\cite{CNNSVD}, leading to $\sim(k\times in\times out)$ non-zero singular values.
\end{enumerate}
Each method has tradeoffs.  
Method (3) is mathematically sound, but computationally expensive. Method (2) is ambiguous.
For our analysis, because we need thousands of runs, we select method (1), which is the fastest (and is easiest to reproduce).

\paragraph{Normalization of Empirical Matrices.}

Normalization is an important, if underappreciated, practical issue.
Importantly, the normalization of weight matrices does \emph{not} affect the PL fits because $\alpha$ is scale-invariant.
Norm-based metrics, however, do depend strongly on the scale of the weight matrix---that is the point.
%\nred{Indeed, early theoretical work by Bartlett suggests that the test accuracy depends strongly on the ``total size'' of the weight matrics.}
To apply RMT, we usually define $\mathbf{X}$ with a $1/N$ normalization, assuming variance of $\sigma^{2}=1.0$.
%\footnote{For Heavy Tailed theorems, one typically needs a normalization such as \nred{$1/N^{\alpha-1}$. check this}}
Pretrained DNNs are typically initialized with random weight matrices $\mathbf{W}_{0}$, with
 $\sigma^{2}\sim 1/\sqrt{N}$, or some variant, e.g., the Glorot/Xavier normalization~\cite{GloBen10}, or a $\sqrt{2/Nk^2}$ normalization for Convolutional 2D Layers. With this implicit scale, 
we do \emph{not} ``renormalize'' the empirical weight matrices, i.e., we use them as-is.
The only exception is that \emph{we do rescale} the Conv2D pre-activation maps $\mathbf{W}_{i,L}$ 
by $k/\sqrt{2}$ so that they are on the same scale as the Linear / Fully Connected (FC) layers.

\paragraph{Special consideration for NLP models.}

NLP models, and other models with large initial embeddings, require special care because the embedding layers frequently lack the implicit $1/\sqrt{N}$ normalization present in other layers.
For example, in GPT, for most layers, the maximum eigenvalue $\lambda_{max}\sim\mathcal{O}(10-100)$, but in the first embedding layer, the maximum eigenvalue is of order $N$ (the number of words in the embedding), or $\lambda_{max}\sim\mathcal{O}(10^{5})$.  
For GPT and GPT2, we treat all layers as-is (although one may want to normalize the first 2 layers $\mathbf{X}$ by $1/N$, or to treat them as outliers).

\subsection{Reproducing Sections \ref{sxn:cv} and \ref{sxn:nlp} }   %% \subsection{Reproducing Sections 4 and 5}

We provide a github repository for this paper that includes Jupyter notebooks that fully reproduce all results (as well as many other results)~\cite{kdd20_sub_repo}.
All results have been produced using the \emph{WeightWatcher} tool (v0.2.7)~\cite{weightwatcher_package}.
The ImageNet and OpenAI GPT pretrained models are provided in the current 
pyTorch~\cite{pytorch} and Huggingface~\cite{huggingface} distributions, as specified in the \texttt{requirements.txt}~file.

@@

\subsection{Reproducing Figure~\ref{fig:resnet204D5L}, for the Distiller Model}

In the \texttt{distiller} folder of our github repo, 
we provide the original Jupyter Notebooks, which use the Intel \texttt{distiller} framework~\cite{distiller}.   % \footnote{\url{https://nervanasystems.github.io/distiller}} 
Figure~\ref{fig:resnet204D5L} is from the  \texttt{``...-Distiller-ResNet20.ipynb''} notebook (see Table~\ref{table:notebooks}).  
For completeness, we provide both the results described here, as well as additional results on other pretrained and distilled models using the \emph{WeightWatcher} tool.

\subsection{Reproducing Table~\ref{table:results} in Section~\ref{sxn:all_cv_models} }

In the \texttt{ww-colab} folder of our github repo, we provide several Google Colab notebooks which can be used to reproduce the results of Section~\ref{sxn:all_cv_models}.
The ImageNet-1K and other pretrained models are taken from the pytorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The data for each regression can be generated in parallel by running each Google Colab notebook (i.e., \texttt{ww\_colab\_0\_100.ipynb}) simultaneously on the same account.
The data generated are analyzed with \texttt{ww\_colab\_results.ipynb}, which runs all regressions and which tabulates the results presented in Table~\ref{table:results}.

@@

\begin{table}[t]
\small
\begin{center}
%KDD% \begin{tabular}{|p{2in}|c|}
\begin{tabular}{|p{3in}|c|}
\hline
Architecture & $\#$ of Models \\
\hline
ResNet                                     & 30 \\
SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt    & 24 \\
DIA-ResNet/DIA-PreResNet                   & 18 \\
ResNeXt                                    & 12 \\
WRN                                        & 12 \\
DLA                                        & 6 \\
PreResNet                                  & 6 \\
ProxylessNAS                               & 6 \\
VGG/BN-VGG                                 & 6 \\
IGCV3                                      & 6 \\
EfficientNet                               & 6 \\
SqueezeNext/SqNxt                          & 6 \\
ShuffleNet                                 & 6 \\
DRN-C/DRN-D                                & 6 \\
ESPNetv2                                   & 6 \\
HRNet                      z                & 6 \\
SqueezeNet/SqueezeResNet                   & 6 \\
\hline
\end{tabular}
\end{center}
\caption{Architectures used}
\label{table:architectures}
\end{table}

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        %OLD% \includegraphics[width=2.5cm]{img/imagenet1k_alpha.png}
        %KDD% \includegraphics[width=2.5cm]{img/all-imagenet-1k_alpha.png}
        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    %KDD% 
    \qquad
    \subfigure[ CIFAR 10 ]{
        %OLD% \includegraphics[width=2.5cm]{img/cifar10_alpha.png}
        %KDD% \includegraphics[width=2.5cm]{img/all-cifar-10_alpha.png}
        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    %KDD% 
    \qquad
    \subfigure[ CIFAR 100 ]{
        %OLD% \includegraphics[width=2.5cm]{img/cifar100_alpha.png}
        %KDD% \includegraphics[width=2.5cm]{img/all-cifar-100_alpha.png}
        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    %KDD% 
    \qquad
    \subfigure[ SVHN ]{
        %OLD% \includegraphics[width=2.5cm]{img/svhn_alpha.png}
        %KDD% \includegraphics[width=2.5cm]{img/all-svhn_alpha.png}
        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    %KDD% 
    \qquad
    \subfigure[ CUB 200 ]{
        %OLD% \includegraphics[width=2.5cm]{img/cub200_alpha.png}
        %KDD% \includegraphics[width=2.5cm]{img/all-cub-200-2011_alpha.png}
        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{% 
             %\charles{Preliminary charts:} 
             PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for five different data sets.
            }
    \label{fig:DSalphas}
\end{figure}

@@

\begin{table}[t]
%KDD% \footnotesize  % \small
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 imagenet-1k & ResNet  & 5.96 &  11.03 & \textbf{3.51} & 4.01 \\
 imagenet-1k & EfficientNet  & 2.67 &  \textbf{1.23} & 2.56 & 2.50 \\
 imagenet-1k & PreResNet  & 6.59 &  15.44 & \textbf{3.59} & 3.71 \\
 imagenet-1k & ShuffleNet  & 35.38 &  89.58 & 19.54 & \textbf{18.48} \\
 imagenet-1k & VGG  & 0.84 &  \textbf{0.68} & 1.89 & 1.59 \\
 imagenet-1k & DLA  & 22.41 &  \textbf{8.49} & 14.69 & 15.68 \\
 imagenet-1k & HRNet  & 0.47 &  0.51 & \textbf{0.16} & 0.16 \\
 imagenet-1k & DRN-C  & 0.60 &  0.66 & \textbf{0.40} & 0.48 \\
 imagenet-1k & SqueezeNext  & 21.94 &  21.39 & 13.31 & \textbf{13.23} \\
 imagenet-1k & ESPNetv2  & 13.77 &  14.74 & \textbf{1.87} & 2.53 \\
 imagenet-1k & IGCV3  & 1.94 &  87.76 & 8.48 & \textbf{1.09} \\
 imagenet-1k & ProxylessNAS  & \textbf{0.19} &  0.26 & 0.28 & 0.26 \\
 imagenet-1k & SqueezeNet  & 0.11 &  0.11 & \textbf{0.07} & 0.08 \\
\hline
 cifar-10 & ResNet  & 0.31 &  0.30 & \textbf{0.28} & 0.28 \\
 cifar-10 & DIA-ResNet  & \textbf{0.05} &  0.08 & 0.28 & 0.32 \\
 cifar-10 & SENet  & 0.09 &  0.09 & \textbf{0.04} & 0.04 \\
\hline
 cifar-100 & ResNet  & 4.13 &  4.50 & \textbf{3.06} & 3.06 \\
 cifar-100 & DIA-ResNet  & \textbf{0.36} &  1.38 & 0.93 & 1.02 \\
 cifar-100 & SENet  & 0.36 &  0.43 & \textbf{0.26} & 0.26 \\
 cifar-100 & WRN  & 0.14 &  0.20 & 0.07 & \textbf{0.06} \\
\hline
 svhn & ResNet  & 0.04 &  0.04 & \textbf{0.02} & 0.02 \\
 svhn & DIA-ResNet  & 0.00 &  \textbf{0.00} & 0.02 & 0.02 \\
 svhn & SENet  & \textbf{0.00} &  0.00 & 0.00 & 0.00 \\
 svhn & WRN  & 0.01 &  0.01 & 0.01 & \textbf{0.01} \\
 svhn & ResNeXt  & 0.00 &  \textbf{0.00} & 0.01 & 0.01 \\
\hline
 cub-200-2011 & ResNet  & 0.20 &  \textbf{0.18} & 3.19 & 3.21 \\
 cub-200-2011 & SENet  & \textbf{1.07} &  1.29 & 1.85 & 1.95 \\
\hline
\end{tabular}
\end{center}
%KDD% 
\vspace{-5mm}
\caption{$MSE$ Results for all CV model regressions. }
\label{table:MSEresults}
\end{table}

\begin{table}[t]
%KDD% \footnotesize  % \small
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
imagenet-1k & ResNet  & 0.82 &  0.67 & \textbf{0.90} & 0.88 \\
 imagenet-1k & EfficientNet  & 0.65 &  \textbf{0.84} & 0.67 & 0.67 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & \textbf{0.85} & 0.85 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & \textbf{0.81} \\
 imagenet-1k & VGG  & 0.71 &  \textbf{0.76} & 0.35 & 0.45 \\
 imagenet-1k & DLA  & 0.13 &  \textbf{0.67} & 0.43 & 0.39 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & \textbf{0.97} & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & \textbf{0.87} & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & \textbf{0.43} \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & \textbf{0.92} & 0.89 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & \textbf{0.99} \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & \textbf{0.38} & 0.26 \\
 imagenet-1k & ProxylessNAS  & \textbf{0.68} &  0.56 & 0.53 & 0.58 \\
\hline
 cifar-10 & ResNet  & 0.58 &  0.59 & \textbf{0.62} & 0.61 \\
 cifar-10 & DIA-ResNet  & \textbf{0.96} &  0.93 & 0.74 & 0.71 \\
 cifar-10 & SENet  & 0.91 &  0.91 & \textbf{0.96} & 0.96 \\
\hline
 cifar-100 & ResNet  & 0.61 &  0.58 & \textbf{0.71} & 0.71 \\
 cifar-100 & DIA-ResNet  & \textbf{0.96} &  0.85 & 0.90 & 0.89 \\
 cifar-100 & SENet  & 0.97 &  0.96 & \textbf{0.98} & 0.98 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & \textbf{0.69} \\
\hline
 svhn & ResNet  & 0.69 &  0.70 & \textbf{0.82} & 0.81 \\
 svhn & DIA-ResNet  & 0.94 &  \textbf{0.95} & 0.78 & 0.77 \\
 svhn & SENet  & \textbf{0.99} &  0.96 & 0.98 & 0.98 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & \textbf{0.21} \\
 svhn & ResNeXt  & 0.87 &  \textbf{0.90} & 0.64 & 0.75 \\
\hline
 cub-200-2011 & ResNet  & 0.94 &  \textbf{0.95} & 0.08 & 0.08 \\
 cub-200-2011 & SENet  & \textbf{0.66} &  0.59 & 0.41 & 0.38 \\
\hline
\end{tabular}
\end{center}
%KDD% 
\vspace{-5mm}
\caption{$R^{2}$ Results for all CV model regressions. }
\label{table:R2results}
\end{table}

@@

>>>>

%\section{Reproducibility Appendix}
\section{Supplementary Information}
\label{sxn:appendix}

\subsection{Supplementary Tables}

\paragraph{Reproducing Sections \ref{sxn:cv} and \ref{sxn:nlp}. }

We provide a github repository for this paper that includes Jupyter notebooks that fully reproduce all results (as well as many other results)~\cite{kdd20_sub_repo}.
All results have been produced using the \texttt{WeightWatcher} tool (v0.2.7)~\cite{weightwatcher_package}.
The ImageNet and OpenAI GPT pretrained models are provided in the current 
pyTorch~\cite{pytorch} and Huggingface~\cite{huggingface} distributions, as specified in the \texttt{requirements.txt}~file.

@@

\paragraph{Reproducing Figure~\ref{fig:resnet204D5L}, for the Distiller Model.}

In the \texttt{distiller} folder of our github repo, 
we provide the original Jupyter Notebooks, which use the Intel \texttt{distiller} framework~\cite{distiller}.   % \footnote{\url{https://nervanasystems.github.io/distiller}} 
Figure~\ref{fig:resnet204D5L} is from the  \texttt{``...-Distiller-ResNet20.ipynb''} notebook (see Table~\ref{table:notebooks}).  
For completeness, we provide both the results described here, as well as additional results on other pretrained and distilled models using the \texttt{WeightWatcher} tool.

\paragraph{Reproducing Table~\ref{table:results} in Section~\ref{sxn:all_cv_models}. }

In the \texttt{ww-colab} folder of our github repo, we provide several Google Colab notebooks which can be used to reproduce the results of Section~\ref{sxn:all_cv_models}.
The ImageNet-1K and other pretrained models are taken from the pyTorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The data for each regression can be generated in parallel by running each Google Colab notebook (i.e., \texttt{ww\_colab\_0\_100.ipynb}) simultaneously on the same account.
The data generated are analyzed with \texttt{ww\_colab\_results.ipynb}, which runs all regressions and which tabulates the results presented in Table~\ref{table:results}.

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{3in}|c|}
\hline
Architecture & $\#$ of Models \\
\hline
ResNet                                     & 30 \\
SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt    & 24 \\
DIA-ResNet/DIA-PreResNet                   & 18 \\
ResNeXt                                    & 12 \\
WRN                                        & 12 \\
DLA                                        & 6 \\
PreResNet                                  & 6 \\
ProxylessNAS                               & 6 \\
VGG/BN-VGG                                 & 6 \\
IGCV3                                      & 6 \\
EfficientNet                               & 6 \\
SqueezeNext/SqNxt                          & 6 \\
ShuffleNet                                 & 6 \\
DRN-C/DRN-D                                & 6 \\
ESPNetv2                                   & 6 \\
HRNet                      z                & 6 \\
SqueezeNet/SqueezeResNet                   & 6 \\
\hline
\end{tabular}
\end{center}
\caption{Architectures used}
\label{table:architectures}
\end{table}

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        \includegraphics[width=4.9cm]{img/all-imagenet-1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    \qquad
    \subfigure[ CIFAR 10 ]{
        \includegraphics[width=4.9cm]{img/all-cifar-10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    \qquad
    \subfigure[ CIFAR 100 ]{
        \includegraphics[width=4.9cm]{img/all-cifar-100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    \qquad
    \subfigure[ SVHN ]{
        \includegraphics[width=4.9cm]{img/all-svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    \qquad
    \subfigure[ CUB 200 ]{
        \includegraphics[width=4.9cm]{img/all-cub-200-2011_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{% 
             %\charles{Preliminary charts:} 
             PL exponent $\alpha$ versus reported Top1 Test Accuracies for pretrained DNNs available for five different data sets.
            }
    \label{fig:DSalphas}
\end{figure}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
 imagenet-1k & ResNet  & 5.96 &  11.03 & \textbf{3.51} & 4.01 \\
 imagenet-1k & EfficientNet  & 2.67 &  \textbf{1.23} & 2.56 & 2.50 \\
 imagenet-1k & PreResNet  & 6.59 &  15.44 & \textbf{3.59} & 3.71 \\
 imagenet-1k & ShuffleNet  & 35.38 &  89.58 & 19.54 & \textbf{18.48} \\
 imagenet-1k & VGG  & 0.84 &  \textbf{0.68} & 1.89 & 1.59 \\
 imagenet-1k & DLA  & 22.41 &  \textbf{8.49} & 14.69 & 15.68 \\
 imagenet-1k & HRNet  & 0.47 &  0.51 & \textbf{0.16} & 0.16 \\
 imagenet-1k & DRN-C  & 0.60 &  0.66 & \textbf{0.40} & 0.48 \\
 imagenet-1k & SqueezeNext  & 21.94 &  21.39 & 13.31 & \textbf{13.23} \\
 imagenet-1k & ESPNetv2  & 13.77 &  14.74 & \textbf{1.87} & 2.53 \\
 imagenet-1k & IGCV3  & 1.94 &  87.76 & 8.48 & \textbf{1.09} \\
 imagenet-1k & ProxylessNAS  & \textbf{0.19} &  0.26 & 0.28 & 0.26 \\
 imagenet-1k & SqueezeNet  & 0.11 &  0.11 & \textbf{0.07} & 0.08 \\
\hline
 cifar-10 & ResNet  & 0.31 &  0.30 & \textbf{0.28} & 0.28 \\
 cifar-10 & DIA-ResNet  & \textbf{0.05} &  0.08 & 0.28 & 0.32 \\
 cifar-10 & SENet  & 0.09 &  0.09 & \textbf{0.04} & 0.04 \\
\hline
 cifar-100 & ResNet  & 4.13 &  4.50 & \textbf{3.06} & 3.06 \\
 cifar-100 & DIA-ResNet  & \textbf{0.36} &  1.38 & 0.93 & 1.02 \\
 cifar-100 & SENet  & 0.36 &  0.43 & \textbf{0.26} & 0.26 \\
 cifar-100 & WRN  & 0.14 &  0.20 & 0.07 & \textbf{0.06} \\
\hline
 svhn & ResNet  & 0.04 &  0.04 & \textbf{0.02} & 0.02 \\
 svhn & DIA-ResNet  & 0.00 &  \textbf{0.00} & 0.02 & 0.02 \\
 svhn & SENet  & \textbf{0.00} &  0.00 & 0.00 & 0.00 \\
 svhn & WRN  & 0.01 &  0.01 & 0.01 & \textbf{0.01} \\
 svhn & ResNeXt  & 0.00 &  \textbf{0.00} & 0.01 & 0.01 \\
\hline
 cub-200-2011 & ResNet  & 0.20 &  \textbf{0.18} & 3.19 & 3.21 \\
 cub-200-2011 & SENet  & \textbf{1.07} &  1.29 & 1.85 & 1.95 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{$MSE$ Results for all CV model regressions. }
\label{table:MSEresults}
\end{table}

\begin{table}[t]
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\langle\log\Vert\cdot\Vert_{F}\rangle$ & $\langle\log\Vert\cdot\Vert_{\infty}\rangle$ & $\hat{\alpha}$ & $\langle\log\Vert\cdot\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
imagenet-1k & ResNet  & 0.82 &  0.67 & \textbf{0.90} & 0.88 \\
 imagenet-1k & EfficientNet  & 0.65 &  \textbf{0.84} & 0.67 & 0.67 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & \textbf{0.85} & 0.85 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & \textbf{0.81} \\
 imagenet-1k & VGG  & 0.71 &  \textbf{0.76} & 0.35 & 0.45 \\
 imagenet-1k & DLA  & 0.13 &  \textbf{0.67} & 0.43 & 0.39 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & \textbf{0.97} & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & \textbf{0.87} & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & \textbf{0.43} \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & \textbf{0.92} & 0.89 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & \textbf{0.99} \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & \textbf{0.38} & 0.26 \\
 imagenet-1k & ProxylessNAS  & \textbf{0.68} &  0.56 & 0.53 & 0.58 \\
\hline
 cifar-10 & ResNet  & 0.58 &  0.59 & \textbf{0.62} & 0.61 \\
 cifar-10 & DIA-ResNet  & \textbf{0.96} &  0.93 & 0.74 & 0.71 \\
 cifar-10 & SENet  & 0.91 &  0.91 & \textbf{0.96} & 0.96 \\
\hline
 cifar-100 & ResNet  & 0.61 &  0.58 & \textbf{0.71} & 0.71 \\
 cifar-100 & DIA-ResNet  & \textbf{0.96} &  0.85 & 0.90 & 0.89 \\
 cifar-100 & SENet  & 0.97 &  0.96 & \textbf{0.98} & 0.98 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & \textbf{0.69} \\
\hline
 svhn & ResNet  & 0.69 &  0.70 & \textbf{0.82} & 0.81 \\
 svhn & DIA-ResNet  & 0.94 &  \textbf{0.95} & 0.78 & 0.77 \\
 svhn & SENet  & \textbf{0.99} &  0.96 & 0.98 & 0.98 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & \textbf{0.21} \\
 svhn & ResNeXt  & 0.87 &  \textbf{0.90} & 0.64 & 0.75 \\
\hline
 cub-200-2011 & ResNet  & 0.94 &  \textbf{0.95} & 0.08 & 0.08 \\
 cub-200-2011 & SENet  & \textbf{0.66} &  0.59 & 0.41 & 0.38 \\
\hline
\end{tabular}
\end{center}
\vspace{-5mm}
\caption{$R^{2}$ Results for all CV model regressions. }
\label{table:R2results}
\end{table}

\subsection{Supplementary Figures}

@@

@@

\subsection{Supplementary Discussion: Additional Details on HT-SR Theory}

The original work on HT-SR Theory~\cite{MM18_TR,MM19_HTSR_ICML,MM20_SDM} considered NNs including AlexNet and InceptionV3 (as well as DenseNet, ResNet, and VGG), and it showed that for nearly every $\mathbf{W}$, the (bulk and tail) of the ESDs can be fit to a truncated PL and the PL exponents $\alpha$ nearly all lie within the range $\alpha\in(1.5,5)$.
Our meta-analysis, the main results of which are summarized in this paper, has shown that these results are ubiquitous.
For example, 
upon examining nearly 10,000 layer weight matrices $\mathbf{W}_{l,i}$ across hundreds of different modern pre-trained DNN architectures, the ESD of nearly every $\mathbf{W}$ layer matrix can be fit to a truncated PL:
$70-80\%$ of the time, the fitted PL exponent $\alpha$ lies in the range $\alpha\in(2,4)$; and  
$10-20\%$ of the time, the fitted PL exponent $\alpha$ lies in the range $\alpha< 2$.  
Of course, there are exceptions: in any real DNN, the fitted $\alpha$ may range anywhere from $\sim 1.5$ to $10$ or higher (and, of course, larger values of $\alpha$ may indicate that the PL is not a good model for the data).  
Still, overall, in nearly all large, pre-trained DNNs, the correlations in the  weight matrices exhibit a remarkable Universality, being both Heavy Tailed, and having small---but not too small---PL exponents.
